%---- Required Packages and Functions ----
\documentclass[a4paper,11pt]{article}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage[sfdefault]{roboto}

\setcounter{secnumdepth}{0}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\tcbset{
   frame code={}
   center title,
   left=0pt,
   right=0pt,
   top=0pt,
   bottom=0pt,
   colback=gray!20,
   colframe=white,
   width=\dimexpr\textwidth\relax,
   enlarge left by=-2mm,
   boxsep=4pt,
   arc=0pt,outer arc=0pt,
}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands
\let\oldsection\section

\renewcommand{\section}[1]{
   \vspace{-3mm}
   \oldsection{\textbf\large{#1}}
   \vspace{-1.5mm}
   {\color{gray}\hrule width 0.98\textwidth height 0.1pt}
   \vspace{2mm}
}

\newcommand{\dateString}[1]{
   \textcolor{gray}{\small{#1}}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
   \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \dateString{#4} \\
      \small{#3} &  \small{#2}\\
   \end{tabular*}
   \vspace{-2mm}
}

\newcommand{\cvItem}[1]{
   \item \small #1
}

\newcommand{\achievementItem}[2]{
\vspace{0.5mm}\item
   \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
   \small{\textbullet\ #1} & \dateString{#2}
   \end{tabular*}
   \vspace{-2mm}
}

\newcommand{\multiSkillList}[8]{
   \begin{tabular*}{0.98\textwidth}{@{\extracolsep{\fill}}llll}
      \small{#1} & \small{#2} & \small{#3} & \small{#4} \\
      \small{#5} & \small{#6} & \small{#7} & \small{#8} \\
   \end{tabular*}
}

\renewcommand\labelitemi{}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}

\newcommand{\resumeItemListStart}{
   \begin{justify}
   \begin{itemize}[label={\textbullet}, leftmargin=2ex, labelsep=0.3em, rightmargin=2ex, itemsep=0mm]
   \small
}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}}

\newcommand{\resumeItemSeparator}{\vspace{0.0mm}}
\newcommand{\achievementItemSeparator}{\vspace{-1.0mm}}
\newcommand{\resumeSubheadingSeparator}{\vspace{-1mm}}
\newcommand{\sectionSeparator}{\vspace{-0.5mm}}

\newcommand{\cvsection}[1]{
\vspace{2mm}
\begin{tcolorbox}
   \textbf{\large #1}
\end{tcolorbox}
\vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
%---- End of Packages and Functions ------

%-------------------------------------------

%%%%%% DEFINITIONS %%%%%%%
\newcommand{\name}{Nikolaos Xenakis}
\newcommand{\role}{Senior Software Engineer}
\newcommand{\phone}{+41 78 250 24 08}
\newcommand{\emaila}{nikosxenakis94@gmail.com}
\newcommand{\location}{Zürich, Switzerland}
\newcommand{\linkLinkedin}{\href{https://linkedin.com/in/nikosxenakis}}
\newcommand{\linkWebsite}{\href{https://nikosxenakis.github.io}}

\begin{document}

%----------HEADING-----------------

\begin{tabularx}{\linewidth}{L >{\hspace*{3.2cm}}L} \\
   \textbf{\Large \name} & {\raisebox{0.0\height}{\small \faPhone}\ \phone} \\
   {\Large \role} & \href{mailto:\emaila}{\raisebox{0.0\height}{\small \faEnvelope}\ {\emaila}} \\
   {} & \raisebox{0.0\height}{\small \faMapMarker*}\ { \location} \\
   % {} & \href{https://github.com/nikosxenakis}{\raisebox{0.0\height}{\small \faGithub}\ {nikosxenakis}} \\
   {} & \linkLinkedin{\raisebox{0.0\height}{\small \faLinkedin}\ { linkedin.com/in/nikosxenakis}} \\
   {} & \linkWebsite{\raisebox{0.0\height}{\small \faGlobe}\ { nikosxenakis.github.io}}
\end{tabularx}

%-----------SUMMARY-----------
\begin{justify}
\small
Senior Software Engineer with 7+ years of experience building scalable backend and full-stack systems using Java, Spring Boot, Node.js, and TypeScript. Fast learner with a strong track record of leading projects, improving architecture, and delivering high-impact features.
\end{justify}

\sectionSeparator

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubHeadingListStart

   \resumeSubheading
      {Senior Software Engineer and Project Manager}{Zürich, Switzerland}
      {Sphynx}{February 2024 - September 2025}
      \resumeSubheadingSeparator
      \resumeItemListStart
         \cvItem {Architecting and developing an Incident Response Automation Tool using Java, Spring Boot and PostgreSQL, ensuring high availability, scalability, and reliability for cybersecurity critical workflows.}
         \cvItem {Managing the SecOPERA EU project on behalf of Sphynx, collaborating with 10 other EU organisations.}
      \resumeItemListEnd

   \resumeItemSeparator

   \resumeSubheading
      {Senior Software Engineer}{Edinburgh, United Kingdom}
      {Welbot}{November 2022 - February 2024}
      \resumeSubheadingSeparator
      \resumeItemListStart
         \cvItem {Engineered state-of-the-art well-being products tailored for enterprises with Node.js, TypeScript, React and AWS, used daily by 20K users.}
         \cvItem {Established an SDLC process and implemented CI/CD pipelines using GitHub Actions, enabling weekly releases.}
         \cvItem {Automated infrastructure with Terraform, deploying AWS environments with sub-5-minute provisioning times.}
         \cvItem {Successfully led two major product releases in one year, migrating to a new infrastructure and codebase.}
      \resumeItemListEnd

   \resumeItemSeparator

   % \resumeSubheading
   %     {Senior Software Engineer}{Edinburgh, United Kingdom}
   %     {SeeByte}{August 2021 - November 2022}
   %     \resumeSubheadingSeparator
   %     \resumeItemListStart
   %         \cvItem {Directed the company-wide CI/CD initiative, implementing Jenkins pipelines and integrating approximately 80 projects.}
   %         \cvItem {Led projects, using Java and .NET, delivering 100\% of them ahead of schedule.}
   %     \resumeItemListEnd

   % \resumeItemSeparator

   % \resumeSubheading
   %     {Software Engineer}{Edinburgh, United Kingdom}
   %     {SeeByte}{September 2019 - August 2021}
   %     \resumeSubheadingSeparator
   %     \resumeItemListStart
   %         \cvItem {Developed the Mission Planning and Analysis software for Unmanned Underwater Vehicles using Java, .NET and C++, enabling interoperability across 6 different UUV vendors.}
   %         \cvItem {Demonstrated products in real-world operational scenarios, resulting in a 100\% contract extension rate.}
   %         \cvItem {Rapidly promoted to the senior level in under 2 years, becoming the fastest promotion in the company.}
   %     \resumeItemListEnd

   \resumeSubheading
      {Senior Software Engineer (Promoted from Software Engineer)}{Edinburgh, United Kingdom}
      {SeeByte}{September 2019 - November 2022}
      \resumeSubheadingSeparator
      \resumeItemListStart
         \cvItem {Developed mission planning and analysis software for Unmanned Underwater Vehicles using Java, .NET and C++, enabling interoperability across 6 different UUV vendors.}
         \cvItem {Participated in real-world sea trials and client demonstrations, contributing to a 100\% contract extension rate.}
         \cvItem {Achieved the fastest promotion in the company, moving from Software Engineer to Senior in under 2 years.}
         \cvItem {Led company-wide CI/CD improvements, implementing Jenkins pipelines and integrating approximately 80 projects to improve release reliability.}
         \cvItem {Delivered multiple engineering projects ahead of schedule, collaborating across research and product teams.}
      \resumeItemListEnd

   \resumeItemSeparator

   \resumeSubheading
      {Software Engineer}{Athens, Greece}
      {Wings ICT Solutions}{April 2017 - September 2018}
      \resumeSubheadingSeparator
      \resumeItemListStart
         \cvItem {Modernized the National Bank of Greece’s CRM by migrating an Objective-C codebase to Angular and TypeScript.}
         \cvItem {Led and delivered an internal bank project for customer application management, working in a team of three engineers.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\sectionSeparator


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
   \resumeSubheading
      % {MSc in High Performance Computing with Data Science}{75\% (Distinction)}
      {MSc in High Performance Computing with Data Science}{Distinction}
      {University of Edinburgh, United Kingdom}{September 2018 - September 2019}

   \resumeItemSeparator
   
   \resumeSubheading
      % {BSc in Computer Science}{84\% (First-Class Honours)}
      {BSc in Computer Science}{First-Class Honours}
      {University of Crete, Greece}{September 2012 - June 2016}

\resumeSubHeadingListEnd

\sectionSeparator

%-----------AWARDS-----------
\section{Awards}
\resumeSubHeadingListStart

\achievementItem
   {Best Academic Performance Award - graduated with the highest grades in the MSc program.}
   {2019}

\achievementItemSeparator

\achievementItem
   % {`Highly Skilled Workforce Scholarship` - full MSc tuition scholarship (£30K), awarded for academic excellence.}
   {Highly Skilled Workforce Scholarship - £30K MSc tuition awarded for academic excellence.}
   {2018}

\achievementItemSeparator

\achievementItem
   % {`Stelios Orfanoudakis Scholarship` - awarded annually for three years as a top-three BSc student (€10K).}
   {Stelios Orfanoudakis Scholarship - awarded for three years as a top-three BSc student (€10K).}
   {2014 - 2016}

\resumeSubHeadingListEnd

\section{Skills}

%-----------SKILLS-----------
\multiSkillList
   {Java}{Spring Boot}{Node.js}{TypeScript}
   {AWS}{GitHub CI/CD}{Kafka}{Event-driven architecture}
%    {.NET}{React}{Angular}{Terraform}{distributed systems}{Docker}

\end{document}